\mytitle

### 2015-08-05 MSc_diss.tex
Almost finished section about O3 sensitivity to total ANs

The lifetimes of alkyl nitrates depend on the seasonality of the photolysis and $OH$ sink, which in turn vary with latitude and altitude. According to \citep{Clemitshaw1997} and \citep{Turberg1990} alkyl nitrates have atmospheric lifetimes of several days to several years, which makes them temporary reservoirs for the short lived $NO_x$ compounds. Being transported from polluted areas to remote background regions and eventually destroyed alkyl nitrates can 'release' $NO_2$ back to the atmosphere, thereby contributing to tropospheric ozone formation.
\subsection{Ozone, alkyl nitrates and carbon bonds}
In the previous sections we covered the chemistry that controls the production of $O_3$ in the troposphere. A traditional way to assess the efficiency of this production is to calculate the ratio:
\begin{equation}\label{eq:OPE}
OPE = \dfrac{k_{HO_2+NO}[HO_2][NO]}{k_{OH+NO_2}[OH][NO_2]} = \dfrac{P_{O_3}}{L_{NO_x}}
\end{equation}
where $OPE$ is the ozone production efficiency, $k_{HO_2+NO}$ - the rate coefficient of reaction (\ref{reac:HO2+NO=NO2+OH}), $k_{OH+NO_2}$ - the rate coefficient of reaction (\ref{reac:OH+NO2=HNO3}), $[X]$ - mixing ratios of corresponding species, $P_{O_3}$ – the $O_3$ production rate, $L_{NO_x}$ – the $NO_x$ loss rate. $OPE$ is determined by the amount of $HO_2$ reacting with $NO$ to form $NO_2$ and $OH$ (i.e., $k_{HO_2+NO}[HO_2][NO]$, (\ref{reac:HO2+NO=NO2+OH})) and the amount of $NO_x$ removed from the system by reaction of $OH$ with $NO_2$ to form nitric acid ($HNO_3$, reaction (\ref{reac:OH+NO2=HNO3})). In other words, $OPE$ shows the amount of ozone created ($P_{O_3}$) per molecule of $NO_x$ removed ($L_{NO_x}$) from the system \citep{Jacob1999}. Due to the reasons described in section \ref{sec:chem_mech} (comment at the bottom of the page!"No representation of the nitric acid ($HNO_3$) in the model"), we use another expression for calculations of the $O_3$ production efficiency. This expression has been recently proposed by Professor Matthew Evans (University of York) amid the mounting concerns about the need of thorough intercomparison of chemical mechanisms of global atmospheric models (including those used in the IPCC reports), why it is more universal and applicable to any kind of model.

@@

The best way to illustrate the central features of the relationship between $O_3$, $NO_x$ and $VOC$ mentioned above is to construct a ozone isopleth plot in a form shown in Figure \ref{fig:Sillman1999}. The isopleth plot shows that the rate of $O_3$ production is a nonlinear function of the $NO_x$ and $VOC$ concentrations. When $VOC$/$NO_x$ ratios are high, the $O_3$ production rate increases with increasing $NO_x$ eventually reaching a local maximum, and decreasing afterwards as $NO_x$ concentrations continue to increase. The local maximum (the 'ridge line') defines the split into $NO_x$-sensitive and $VOC$-sensitive regimes. Under the 'ridge line' the $VOC$/$NO_x$ ratios are high, and the $O_3$ production rate increases with increasing $NO_x$ and almost insensitive to $VOC$. Above the 'ridge line' the $VOC$/$NO_x$ ratios are low, and the $O_3$ production rate increases with increasing $VOC$ and decreases with increasing $NO_x$ \citep{Sillman2013}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure} % Sillman1999withdotsline and netO3rate_withINORG_NOx_1ppb_100ppb
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{{./pics/Sillman1999_Fig1_adapted_withdotsrectangle}.png}
  \captionof{figure}{Isopleths giving net rate of $O_3$ production (ppb/h, solid lines) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) for mean summer daytime meteorology and clear skies. The solid lines represent production rates of 1, 2.5, 5, 10, 15, 20 and 30 ppb/h. Adapted from \citep{Sillman1999}.}\label{fig:Sillman1999}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3rate_withINORG_NOx_1ppb_100ppb.png}
  \captionof{figure}{Isopleths giving net rate of $O_3$ production (ppb/h, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) in the first modelling experiment with alkyl nitrate chemistry switched off combined with an additional run with inorganic chemistry only (i.e. the only $VOC$ is $CO$).}\label{fig:noAN_netO3rate}
\end{minipage}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Rewrite!

@@

\begin{figure} % netO3rate noAN withAN diff
\centering
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3rate_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3rate_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3ratediff_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\caption{Isopleths giving net rate of $O_3$ production (ppb/h, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) with alkyl nitrate chemistry switched off (left) and switched on (middle). Difference between them is shown on the right.}\label{fig:netO3rate_noAN_withAN_diff}
As expected, the inclusion of alkyl nitrate chemistry slows down the net $O_3$ production rate. At low $NO_x$ and $VOCs$ initial levels, this slowdown is -0.2...-0.6 ppb of $O_3$ per hour. As $NO_x$ and $VOCs$ levels increase the $O_3$ production rate decreases, reaching the maximum decrease of -1.94 ppb of $O_3$ per hour at 100 ppb of $NO_x$ and $VOCs$ level from case I (not the highest $VOCs$ level). At the range of $NO_x$ levels from 1 ppb to 10 ppb the $O_3$ production rate is slightly more sensitive to $VOCs$ levels, while it is almost insensitive to $VOCs$ at $NO_x$ levels higher than 10 ppb and 2050 ppbC of $VOCs$. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure} % netO3mixrat noAN allAN diff
\centering
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3mixrat_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3mixrat_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3mixratdiff_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\caption{Isopleths giving net $O_3$ production (ppb, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) with alkyl nitrate chemistry switched off (left) and switched on (middle). Difference between them is shown on the right. Net production = final - initial value of $O_3$ mixing ratio.}\label{fig:netO3mixrat_noAN_withAN_diff}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The change in net rate of $O_3$ production due to inclusion of alkyl nitrate chemistry into the chemical mechanism has a direct impact on absolute $O_3$ levels calculated by the model. Figure \ref{fig:netO3mixrat_noAN_withAN_diff} shows that the net $O_3$ production (difference between final and initial $O_3$ mixing ratio) is smaller when alkyl nitrate chemistry is switched on. At low $NO_x$ and $VOCs$ levels the (negative) change in the net $O_3$ production is 5-10 ppb, at high $NO_x$ and $VOCs$ levels it is 35-45 ppb (per 24 hours) with maximum value of 46.5 ppb. However, these changes in the net $O_3$ production should be treated with care, because the model due to reasons described in Section \ref{sec:method} gives unrealistically high $O_3$ mixing ratios (maximum 650 ppb while typical maximum urban $O_3$ mixing ratio (Los Angeles, Mexico City) is 490 ppb (http://www-personal.umich.edu/~sillman/ozone.htm). Therefore, in this case a more useful estimate of effect of these changes is to express them in percentage form (i.e., compare like with like), and it appears that these changes are very small: ??? respectively.

To see what caused these changes it is useful to look at the net production of the sum of the alkyl nitrates themselves as a function of $NO_x$ and $VOCs$ levels (Figure \ref{fig:endtotalANs}). Since alkyl nitrates are the only sink for $NO_x$ in our model high production of these species was expected. The range is from 0.2 ppb to 1.4 ppb for the range of $NO_x$ levels inspected from 250 ppt to 100 ppb.
However, real concentrations reported from observational studies are of different order, tens of ppt.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure} % endtotalANs
\includegraphics[width=.5\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_endtotalANs_noINORG_NOx_250ppt_100ppb.png}
\caption{Isopleths of net production of alkyl nitrates ($\Sigma RONO_2$) as a function of $NO_x$ and $VOCs$ levels.}\label{fig:endtotalANs}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
! Dependence of alkyl nitrate yield on carbon number (paper about n-alkanes): bigger yield of ANs from larger carbon number means that the potential for contributing to photochemical air pollution may be less for the larger (C>6) n-alkanes that for the smaller ones.

@@

As it has been noted in section \ref{sec:intro_ANs}, there is a way to estimate the $O_3$ production per carbon bond emitted into the system and relate it to the alkyl nitrate chemistry. Such calculations have been first conducted by \citep{Evans2014} for the global 3D chemistry-climate model GEOS-Chem\citep{Bey2001}. They estimated that $\epsilon$ value for the GEOS-Chem model in simulation with full chemistry is equal to 0.2 meaning that to produce 1 molecule of $O_3$ 0.2 carbon bonds should have been emitted. They also estimated that in simulation with $CH_4$ only $\epsilon$ is equal to 0.3, meaning that more carbon bonds should have been emitted to produce the same amount of $O_3$.

>>>>

The lifetimes of alkyl nitrates depend on the seasonality of the photolysis and $OH$ sink, which in turn vary with latitude and altitude. According to \citep{Clemitshaw1997} and \citep{Turberg1990} alkyl nitrates have atmospheric lifetimes of several days to several years, which makes them temporary reservoirs for the short lived $NO_x$ compounds. Being transported from polluted areas to remote background regions and eventually destroyed alkyl nitrates can 'release' $NO_2$ back to the atmosphere, thereby contributing to tropospheric ozone formation.
\subsection{Ozone, alkyl nitrates and carbon bonds}\label{sec:intro_CB}
In the previous sections we covered the chemistry that controls the production of $O_3$ in the troposphere. A traditional way to assess the efficiency of this production is to calculate the ratio:
\begin{equation}\label{eq:OPE}
OPE = \dfrac{k_{HO_2+NO}[HO_2][NO]}{k_{OH+NO_2}[OH][NO_2]} = \dfrac{P_{O_3}}{L_{NO_x}}
\end{equation}
where $OPE$ is the ozone production efficiency, $k_{HO_2+NO}$ - the rate coefficient of reaction (\ref{reac:HO2+NO=NO2+OH}), $k_{OH+NO_2}$ - the rate coefficient of reaction (\ref{reac:OH+NO2=HNO3}), $[X]$ - mixing ratios of corresponding species, $P_{O_3}$ – the $O_3$ production rate, $L_{NO_x}$ – the $NO_x$ loss rate. $OPE$ is determined by the amount of $HO_2$ reacting with $NO$ to form $NO_2$ and $OH$ (i.e., $k_{HO_2+NO}[HO_2][NO]$, (\ref{reac:HO2+NO=NO2+OH})) and the amount of $NO_x$ removed from the system by reaction of $OH$ with $NO_2$ to form nitric acid ($HNO_3$, reaction (\ref{reac:OH+NO2=HNO3})). In other words, $OPE$ shows the amount of ozone created ($P_{O_3}$) per molecule of $NO_x$ removed ($L_{NO_x}$) from the system \citep{Jacob1999}. Due to the reasons described in section \ref{sec:chem_mech} (comment at the bottom of the page!"No representation of the nitric acid ($HNO_3$) in the model"), we use another expression for calculations of the $O_3$ production efficiency. This expression has been recently proposed by Professor Matthew Evans (University of York) amid the mounting concerns about the need of thorough intercomparison of chemical mechanisms of global atmospheric models (including those used in the IPCC reports), why it is more universal and applicable to any kind of model.

@@

The best way to illustrate the central features of the relationship between $O_3$, $NO_x$ and $VOC$ mentioned above is to construct a ozone isopleth plot in a form shown in Figure \ref{fig:Sillman1999}. The isopleth plot shows that the rate of $O_3$ production is a nonlinear function of the $NO_x$ and $VOC$ concentrations. When $VOC$/$NO_x$ ratios are high, the $O_3$ production rate increases with increasing $NO_x$ eventually reaching a local maximum, and decreasing afterwards as $NO_x$ concentrations continue to increase. The local maximum (the 'ridge line') defines the split into $NO_x$-sensitive and $VOC$-sensitive regimes. Under the 'ridge line' the $VOC$/$NO_x$ ratios are high, and the $O_3$ production rate increases with increasing $NO_x$ and almost insensitive to $VOC$. Above the 'ridge line' the $VOC$/$NO_x$ ratios are low, and the $O_3$ production rate increases with increasing $VOC$ and decreases with increasing $NO_x$ \citep{Sillman2013}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure} % Sillman1999withdotsline and netO3rate_withINORG_NOx_1ppb_100ppb
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{{./pics/Sillman1999_Fig1_adapted_withdotsrectangle}.png}
  \captionof{figure}{Isopleths giving net rate of $O_3$ production (ppb/h, solid lines) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) for mean summer daytime meteorology and clear skies. The solid lines represent production rates of 1, 2.5, 5, 10, 15, 20 and 30 ppb/h. Adapted from \citep{Sillman1999}.}\label{fig:Sillman1999}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3rate_withINORG_NOx_1ppb_100ppb.png}
  \captionof{figure}{Isopleths giving net rate of $O_3$ production (ppb/h, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) in the first modelling experiment with alkyl nitrate chemistry switched off combined with an additional run with inorganic chemistry only (i.e. the only $VOC$ is $CO$).}\label{fig:noAN_netO3rate}
\end{minipage}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Rewrite!

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure} % netO3rate noAN withAN diff
\centering
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3rate_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3rate_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3ratediff_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\caption{Isopleths giving net rate of $O_3$ production (ppb/h, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) with alkyl nitrate chemistry switched off (left) and switched on (middle). Difference between them is shown on the right.}\label{fig:netO3rate_noAN_withAN_diff}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

As expected, the inclusion of alkyl nitrate chemistry slows down the net $O_3$ production rate. At low $NO_x$ and $VOCs$ initial levels, this slowdown is -0.2...-0.6 ppb of $O_3$ per hour. As $NO_x$ and $VOCs$ levels increase the $O_3$ production rate decreases, reaching the maximum decrease of -1.94 ppb of $O_3$ per hour at 100 ppb of $NO_x$ and $VOCs$ level from case I (not the highest $VOCs$ level). At the range of $NO_x$ levels from 1 ppb to 10 ppb the difference in $O_3$ production rate is slightly more sensitive to $VOCs$ levels, while it is almost insensitive to $VOCs$ at $NO_x$ levels higher than 10 ppb and 2050 ppbC of $VOCs$. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure} % netO3mixrat noAN allAN diff diffpercent
\centering
\begin{minipage}{.4\textwidth} % noAN
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3mixrat_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.4\textwidth} % diff
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3mixratdiff_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.4\textwidth} % allAN
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3mixrat_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.4\textwidth} % diffpercent
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3mixratdiffpercent_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\caption{Isopleths giving net $O_3$ production (ppb, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb, range 250 ppt - 100 ppb) with alkyl nitrate chemistry switched off (a) and switched on (b). Absolute difference (with alkyl nitrates minus without them) between two series of model runs in ppb (c), same in \% (d). Net production = final - initial value of $O_3$ mixing ratio.}\label{fig:netO3mixrat_noAN_withAN_diff}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The change in net rate of $O_3$ production due to inclusion of alkyl nitrate chemistry into the chemical mechanism has a direct impact on absolute $O_3$ levels calculated by the model. Figure \ref{fig:netO3mixrat_noAN_withAN_diff} shows that the net $O_3$ production (difference between final and initial $O_3$ mixing ratio) is smaller when alkyl nitrate chemistry is switched on. At low $NO_x$ and $VOCs$ levels the negative (!) change in the net $O_3$ production is 5-10 ppb, at high $NO_x$ and $VOCs$ levels it is 35-45 ppb (per 24 hours) with maximum value of 46.5 ppb.

These changes in the net $O_3$ production should be treated with care, because the model due to reasons described in Section \ref{sec:method} gives unrealistically high $O_3$ mixing ratios. The maximum $O_3$ mixing ratio in the model is equal to 650 ppb (at the highest $NO_x$ level (100 ppb) and the lowest $VOCs$ level (case A)), while maximum typical urban (Los Angeles, Mexico City) $O_3$ mixing ratio is 490 ppb (http://www-personal.umich.edu/~sillman/ozone.htm). Therefore, a more useful estimate is a percentage difference in $O_3$ mixing ratios between two series of model runs shown in Figure \ref{fig:netO3rate_noAN_withAN_diff} DDDDD!. It appears that the largest absolute changes in $O_3$ mixing ratios (40-45 ppb) are changes by only 20-30\%, while changes up to 90\% take place the model is in low $NO_x$ and high $VOCs$ conditions.

To see what caused these changes it is useful to look at the net production of the sum of the alkyl nitrates themselves as a function of $NO_x$ (250 ppt - 100 ppb) and $VOCs$ (Figure \ref{fig:endtotalANs}). Since alkyl nitrates are the only sink for $NO_x$ in our model high production of these species was expected. The $NO_x$-$VOC$ field of total $RONO_2$ isopleths is mostly characterized by mixing ratios of ppb level (0.2-1.4 ppb), while the observations show that their mean mixing ratios lay at a level of tens-thousands of ppt (Table \ref{tab:ANmean}). Nevertheless, Figure \ref{fig:endtotalANs} will be of interest to other researches, because it is probably the first ever attempt to derive the distribution of $\Sigma RONO_2$ mixing ratios in $NO_x$-$VOC$ field.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure} % endtotalANs
\includegraphics[width=.5\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_endtotalANs_noINORG_NOx_250ppt_100ppb.png}
\caption{Isopleths of net production of alkyl nitrates ($\Sigma RONO_2$) as a function of $NO_x$ and $VOCs$ levels.}\label{fig:endtotalANs}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
! Dependence of alkyl nitrate yield on carbon number (paper about n-alkanes): bigger yield of ANs from larger carbon number means that the potential for contributing to photochemical air pollution may be less for the larger (C>6) n-alkanes that for the smaller ones.

@@

As it has been noted in section \ref{sec:intro_CB}, there is a way to estimate the $O_3$ production per carbon bond emitted into the system and relate it to the alkyl nitrate chemistry. Such calculations have been first conducted by \citep{Evans2014} for the global 3D chemistry-climate model GEOS-Chem \citep{Bey2001}. They estimated that $\epsilon$ value for the GEOS-Chem model in simulation with full chemistry is equal to 0.2 meaning that to produce 1 molecule of $O_3$ 0.2 carbon bonds should have been emitted. They also estimated that in simulation with $CH_4$ only $\epsilon$ is equal to 0.3, meaning that more carbon bonds should have been emitted to produce the same amount of $O_3$.
